Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-05-02 paper.tex

\usepackage{cvpr2019AuthorKit/latex/cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
% \usepackage{arydshln}
% \usepackage{todonotes}

@@

%%% Datasets and SOTA
Influenced by the recent advancements on person re-id vehicle re-id has started
to gain increasing attention, 
and a number of vehicle databases and additional labeling are now available to
facilitate this research
 including 
 VeRi-776\cite{Liu2016icme-veri, Liu2016eccv_veri}  ,
 VehicleID\cite{liu2016vehicleid} and VRIC\cite{kanaci2018vehicle} and methods
 specific to vehicle re-ID becoming more frequent in various venues
 \cite{wang2017orientation, Shen_2017_ICCV, Zhou2018VAMI}.

%%% Our method:
In this paper we propose a new mutual learning based network architecture, that
aims to simultaneously learn a number of tasks, plus a consensus, to build an
improved representation for the purpose of vehicle re-identification.
% Second, we propose to leverage multi-task learning to gen- erate discriminative
% feature representation by the joint op- timization of group sensitive triplet
% loss and softmax loss, which can be well applied to accomplish large scale
% vehicle re-identification towards real applications.

@@

In order to perform Re-ID of previously unseen query vehicles, the aim of our
model is to learn an feature embedding that allows for accurate retrivals based
on distance (\eg L1) from the query image representation. In order to perform
this task, we utilise training data containing a number of different labels:
identity class labels, vehicle orientation class labels, and landmark position
labels for a number of specific keypoints. We assume two sets of training
examples 
$\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ 
and 
$\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, 
containing $N$ and $M$ training images respectively. Both training sets contain the associated identity class labels 
$\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, 
where $y_i \in \left[1,...,N_{id}\right]}$ for $N_{id}$ 
distinct vehicle idenities spanning the two training sets. However, in
addition, $\mathcal{I}_1$ also contains orientation labels,
$\mathcal{O_1}=\{o_i\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ 
is the orientation (for $N_O$ possible orientations).

%and landmark position labels $\mathcal{L_1}=\{\mathbf{l_i}\}_{i=1}^N$ $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $N_L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$

In order to perform accurate re-ID, we use this data to build a model
constructed from a number of branches, each of which is tasked with learning a
specific aspect of the data. \emph{TODO expand}

@@

\paragraph{VeRi776}

\paragraph{VehicleID}

\paragraph{BoxCars21k}

\paragraph{CompCars}

\begin{table}
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    MSVF \cite{kanaci2018vehicle} & 49.3 & 88.6 & - \\
    OIFE \cite{wang2017orientation} & 51.4 & 68.3 & 89.7 \\
    S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
    MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
    \hline
    MTML-S & \\
    MTML-O & \\
    MTML-G & \\
    % \hdashline
    MTML-SG & \\
    MTML-OG & \\
    MTML-OSG & \bf{61.8} & \bf{90.3} & \bf{95.4} \\
    \hline
    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & \bf{94.6} \\
    MTML-OSG (ReRank) & \bf{65.8} & \bf{91.9} & 94.0 \\
    \hline
  \end{tabular}
  \caption{Trained/tested on VeRi776 only}
  \label{T:benchmark_results_veri}
\end{table}

>>>>

\usepackage{cvpr2019AuthorKit/latex/cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
% \usepackage{arydshln}
\usepackage{subcaption}

@@

%%% Datasets and SOTA
Influenced by the recent advancements on person re-id vehicle re-id has started
to gain increasing attention, 
and a number of vehicle databases and additional labeling are now available to
facilitate this research
 including 
 VeRi-776\cite{Liu2016icme-veri, Liu2016eccv_veri},
 VehicleID\cite{liu2016vehicleid} and VRIC\cite{kanaci2018vehicle} and methods
 specific to vehicle re-ID becoming more frequent in various venues
 \cite{wang2017orientation, Shen_2017_ICCV, Zhou2018VAMI}.

%%% Our method:
\todo{Expand near submission}
In this paper we propose a new mutual learning based network architecture, that
aims to simultaneously learn a number of tasks, plus a consensus, to build an
improved representation for the purpose of vehicle re-identification.
% Second, we propose to leverage multi-task learning to gen- erate discriminative
% feature representation by the joint op- timization of group sensitive triplet
% loss and softmax loss, which can be well applied to accomplish large scale
% vehicle re-identification towards real applications.

@@

In order to perform Re-ID of previously unseen query vehicles, the aim of our model is to learn a feature embedding that allows for accurate retrivals based on distance (\eg L1) from the query image representation. In order to perform this task, we utilise training data containing a number of different labels: identity class labels as well as vehicle orientation class labels.
%and landmark position labels for a number of specific keypoints
We assume two sets of training examples $\mathcal{I}_1 = \{\mathbf{I_i}\}_{i=1}^N$ and $\mathcal{I}_2 = \{\mathbf{I_i}\}_{i=1}^M$, containing $N$ and $M$ training images respectively. Both training sets contain the associated identity class labels $\mathcal{Y}_1=\{y_i\}_{i=1}^N$ and $\mathcal{Y}_2=\{y_i\}_{i=1}^M$, where $y_i \in \left[1,...,N_{id}\right]$ for $N_{id}$ distinct vehicle idenities spanning the two training sets. However, in addition, $\mathcal{I}_1$ also contains orientation labels, $\mathcal{O_1}=\{o_i\}_{i=1}^N$, where $o_i \in \left[1,...,N_O\right]$ is the orientation (for $N_O$ possible orientations).
%and landmark position labels $\mathcal{L_1}=\{\mathbf{l_i}\}_{i=1}^N$ $\mathbf{l_i}=\{\left(x_{i,1},y_{i,1}\right),...,\left(x_{i,L},y_{i,L}\right)\}$ defines the position of $N_L$ keypoint landmarks for the vehicle within image $\mathbf{I}_i$, which we normalise according to the image size so that $x,y \in [0,1]$

In order to perform accurate re-ID, we use this data to build a model constructed from a number of branches, each of which is tasked with learning a specific aspect of the data concurrently. The branches of the model are as follows: A) Identity classification B) Identity classification from a scaled image C) Identity from grayscale image D) Identity plus the vehicles' orienations. The individual branches then form a consensus prediction on the identity of the training examples, and this consensus is then employed for regulation of the individual branches.
>>>>>>> e5e018ecb6db264c0f87b6bfce9aaf7c51b0ff67

@@

We employ a number of previously released Vehicle Re-ID datasets in our experiments, in order to train and test our method extensively. Firstly we conduct experiments on two benchmark datasets: VeRi776 and VehicleID. Firstly we train and test only the VeRi776 dataset, for comparison with previous state-of-the-art methods. And secondly we train on both the VeRi776 and VehicleID datasets, and then test on the VehicleID, for all three testsets: small, medium and large. We conduct the latter experiment in this was due to the fact that our method requires some training data with orientation labels. As VeRi776 is the only dataset with labels of this kind, we must therefore include it in the training.

\begin{table*}
  \centering
  \begin{tabular}{c || c | c | c || c | c || c | c}
    \hline
    \multirow{2}{*}{Dataset} & \multicolumn{3}{c||}{Training} & \multicolumn{2}{c||}{Probe} & \multicolumn{2}{c}{Gallery} \\
    \cline{2-7}
    & \#IDs& \#Imgs & \#Orients & \#IDs & \#Imgs & \#IDs & \#Imgs \\
    \hline
    VeRi-776 \cite{} & 576 & 30188 & 8 & 200 & 1678 & 200 & 11579 \\
    VehicleID \cite{} & 13164 & 100182 & - & 2400 & 17638 & 2400 & 2400 \\
    BoxCars \cite{} & 21250 & 63750 & -  & - & - & - & - \\
    CompCars \cite{} & 1118 & 31148 & - & - & - & - & - \\
    AICity2019 \cite{} & \\
    \hline
  \end{tabular}
  \caption{Details of the datasets employed for train and test.}
  \label{T:dataset_details}
\end{table*}

Table \ref{T:benchmark_results_veri} shows the results of the first experiment, where we train and test only on the VeRi776 dataset. As can be seen, our model achieves state-of-the-art mAP and Rank-1 scores on this dataset, of ... and ... respectively.

After 100 epochs

\begin{table}
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    MSVF \cite{kanaci2018vehicle} & 49.3 & 88.6 & - \\
    OIFE \cite{wang2017orientation} & 51.4 & 68.3 & 89.7 \\
    S-CNN+P-LSTM \cite{Shen_2017_ICCV} & 58.3 & 83.5 & 90.0 \\
    MTCRO \cite{xu2018framework} & 61.6 & 87.2 & 94.2 \\
    \hline
    MTML-S & 59.4 & 89.7 & 95.1 \\
    MTML-O & \\
    MTML-G & \\
    % \hdashline
    MTML-SG & 63.4 & 91.1 & 95.4 \\
    MTML-OG & \\
    MTML-OSG & \bf{61.8} & \bf{90.3} & \bf{95.4} \\
    \hline
    MTCRO (ReRank) \cite{xu2018framework} & 62.6 & 88.0 & \bf{94.6} \\
    MTML-OSG (ReRank) & \bf{65.8} & \bf{91.9} & 94.0 \\
    \hline
  \end{tabular}
  \caption{Trained/tested on VeRi776 only}
  \label{T:benchmark_results_veri}
\end{table}
